---
title: 'Chapter 3: Data Visualization'
author: "Mashael"
date: "12/13/2020"
output: html_document
---


#3.2.4 Exercises

```{r}
library(ggplot2)

df <- mpg
```


#Run ggplot(data = mpg). What do you see?

```{r}
ggplot(mpg)

#nothing appear
```

#How many rows are in mpg? How many columns?
```{r}
df
#234 * 11
```

#What does the drv variable describe? Read the help for ?mpg to find out.
```{r}
?mpg

#the typee of drive train:

#f = front-weel drive
#r = rear wheel drive
#4 = 4wd
```

#Make a scatterplot of hwy vs cyl.
```{r}

ggplot(df)+
  geom_point(mapping = aes(x = cyl, y = hwy))


```

#What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
```{r}
ggplot(df)+
  geom_point(mapping = aes(x = class, y = drv))

#scatterplot is for continuous variables and since these two vars are categorical there are few points and we can't read useful info from this plot
```


#3.3.1 Exercises


# What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

```{r}

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```



# Which variables in mpg are categorical? Which variables are continuous?
How can you see this information when you run mpg?
```{r}
str(df)

#Categorical: class, fl, drv,trans, model, manufacturer  
#Continuous:year, displ, cyl, cty, hwy

```


# Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

# we can use color and size for continuous but shape can't be used, in continuous we can use all these three
```{r}
# error mesaage: A continuous variable cannot be mapped to shape
ggplot(df)+
  geom_point(mapping = aes(x = hwy, y = displ, color = cty))


```
```{r}

ggplot(df)+
  geom_point(mapping = aes(x = hwy, y = displ, size = cty))


```


```{r}
ggplot(df)+
  geom_count(mapping = aes(x = class, y = fl, color = drv, size = drv, shape = drv))

```


#What happens if you map the same variable to multiple aesthetics?

# works, but bad visualization

```{r}

ggplot(df)+
  geom_point(mapping = aes(x = hwy,y = displ, color = hwy, size = hwy))


```


# What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
ggplot(df)+
  geom_point(mapping = aes(x = hwy, y = displ),stroke = 5) #change border size
```

# What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.


```{r}
ggplot(df)+
  geom_point(mapping = aes(x = hwy, y = displ, colour = displ < 5))


```


# 3.5.1 Exercises


# What happens if you facet on a continuous variable?

```{r}
ggplot(df)+
  geom_point(mapping = aes(x = hwy, y = displ))+
  facet_wrap(~ cty)

#huge number of facets which is something not readable
```

# What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?

# they don't have observations in emppty facets in the first graph, and points in the second

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```


```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))

```




# What plots does the following code make? What does . do?

# 1. first code will facet x and y based on drv values
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)


```

# 2. will facet cyl based on displ and hwy

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```


# Take the first faceted plot in this section:


What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

some times faceting is more readable when data have multiple categrories and lots of data points which can be overlapped so faceting separate it and maeke seeing the diffrence easeier.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)

```

# Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?


facet_wrap(
  facets,
  nrow = NULL, **number of rows of facets**
  ncol = NULL, 
  scales = "fixed",
  shrink = TRUE,
  labeller = "label_value",
  as.table = TRUE,
  switch = NULL,
  drop = TRUE,
  dir = "h",
  strip.position = "top"
)


```{r}
?facet_wrap

```


#3.6.1 Exercises







