---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
```




this dataset is from TidyTuesday github repository: https://github.com/rfordatascience/tidytuesday

# 1.Data cleaning

```{r}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

```

check if there is null data

```{r}
sum(is.na(coffee_ratings))
```

fixing date columns
change grading date and expiration to mdy format

```{r}
coffee_ratings <- coffee_ratings %>%
  mutate(grading_date = mdy(grading_date),
            expiration = mdy(expiration))

```


fixing some columns with unknown value

```{r}

coffee_ratings <- coffee_ratings %>%
  replace_na(list(owner = "Unknown", farm_name = "Unknown", mill = "Unknown", processing_method = "Washed / Wet"))



```



```{r}
sum(is.na(coffee_ratings$lot_number))
sum(is.na(coffee_ratings$altitude))

coffee_ratings %>%
  count(lot_number, sort = TRUE)

coffee_ratings %>%
  count(altitude, sort = TRUE)


coffee_ratings <- coffee_ratings %>%
                  select(-c(lot_number,altitude))

```

filling NA for altitude_low_meters ,altitude_high_meters ,altitude_mean_meters

```{r}
coffee_ratings %>%
  ggplot(mapping = aes(x = altitude_low_meters))+
  geom_histogram(binwidth = 5000)

```
```{r}
coffee_ratings %>%
                  summarise(altitude_low_median = median(altitude_low_meters, na.rm = TRUE))


coffee_ratings <- coffee_ratings %>% replace_na(list(altitude_low_meters = 1310.64))


```

```{r}
coffee_ratings %>%
  ggplot(mapping = aes(x = altitude_high_meters))+
  geom_histogram(binwidth = 5000)

```

```{r}
coffee_ratings %>%
                  summarise(altitude_high_median = median(altitude_high_meters, na.rm = TRUE))

coffee_ratings <- coffee_ratings %>% replace_na(list(altitude_high_meters = 1350))


```

```{r}

coffee_ratings %>%
  ggplot(mapping = aes(x = altitude_mean_meters))+
  geom_histogram(binwidth = 5000)

```

# this column is the mean of two columns (altitude_high and altitude_low)
```{r}
mean.high.low <- (1310.64	+ 1350)/2

coffee_ratings <- coffee_ratings %>% replace_na(list(altitude_mean_meters = mean.high.low))


```


```{r}
sum(is.null(coffee_ratings)) # zero
```

# 2. Exploratory Data Analysis



```{r}
coffee_ratings %>%
  ggplot(aes(country_of_origin)) + geom_bar() + theme(axis.text.x = element_text(angle = 90))
```



```{r}
coffee_ratings %>%
  ggplot(aes(processing_method)) + geom_bar() + theme(axis.text.x = element_text(angle = 90))
```




















